Turbulence in compact to giant HII regions

### 2021-06-25 mnras_template.tex
LOS vs POS variations
Fix compilation errors
Add missing editor to one reference. Change all \cite{} -> \citet{}

The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas, but despite the previous evidence of this fluctuations not been random, little is understood about their nature. Several problems arise in the study of these fluctuation. Intrinsic with observations there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal}. Other statistical techniques like velocity channel analysis (VCA) \citep{2000ApJ...537..720L} have been proved to better recreate the spectrum of the velocity field \citep{medina2014,arthur2016turbulence}. More recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex. \cite{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds. Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \cite{1981MNRAS.194..809L}.

The non-thermal broadening on the spectral emission lines also has been suggested as evidence of disorder motions along the line-of-sight (LOS). \citet{smith1970} discovered that the line width of GEHRs was supersonic in the order of $\sigma \sim$ 17-26 km s\kms. \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$). They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies. The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening. The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}. This features seems to drive visually the regions with filaments, arcs and shells. On their spectra double and multiple emission features are signature of these objects. \cite{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars. \cite{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

Despite different issues that are related with the nature of the problem of turbulence in HII regions, the vast majority of research using the second-order structure function consider individual regions and hence different methodology. \cite{1987ApJ...317..686O} has determined the structure functions for a sample of galactic HII regions but isn't conclusive about them. The individuality of previous works and the need to understand the relationship between the measured turbulent properties for different classes of HII regions has lead us to develop this investigation.

@@

We use data from \cite{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}. Its physical and kinematics properties along its stellar population are well documented in the review of \cite{2001ARA&A..39...99O}. The main ionizing star is $\theta^{1}$Ori C (spectral type $\sim$O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster. The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.

Archival data from \cite{Damiani:2016a} and \cite{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively.

@@

Using observations observations from \cite{Castro:2018a} (private communication) we study the Tarantula Nebula (30~Dor) in the LMC. At a distance of 49.9 kpc \citep{2013Natur.495...76P} is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}. The star forming region NGC 2070 host the massive star cluster R136.

@@

The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}. \cite{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31). The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon. The cumulative integration time per frame is 36 s with a seeing value of 1''. The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$. Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
The NGC 604 TAURUS-II observations were used by \cite{sabalisck1995supersonic}, \cite{tanco1997} and \cite{2019arXiv191203543M}.

NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments. It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc. It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}. \cite{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.

The stellar population has been identified and classified by \cite{1996ApJ...456..174H} (and references therein). Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population. \citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).  The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}. This suggest that two episodes of star formation, at least, have taken place in the GEHR. \citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.

NGC 595 is the second brightest giant HII region in the M33 galaxy with a length of 300 pc. The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}. \cite{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$. \cite{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \cite{1993AJ....105.1400D}.

It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \cite{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.

@@

%\cite{2002MNRAS.329..481B} 39.42 38.95 38.21 38.30  39.46 37.36  37.08

@@

\begin{table}
\begin{center}\caption{General statistical properties of the centroid velocities. a) \cite{tanco1997} b) \cite{2019arXiv191203543M} c) \cite{Castro:2018a} d) \cite{Damiani:2016a} e) \cite{Damiani:2017b} f) \cite{1987A&A...176..338H} g) \cite{1987A&A...176..347H}.} 
\begin{tabular}{cccccc}\hline
HII    &  $\mu$   & $\sigma^{2}$        &  No. of  &\(s_0\)& Previously  \\
   Region       &  [km/s]  &  [km$^{2}$/s$^{2}$] &  points   &[pc]& used in:\\\hline
NGC 604   &  3.56    &    54.63            &    9 510    &1.73&  a,b     \\
NGC 595   &  2.82    &    44.13            &    8 765    &1.73&  -     \\
Hubble V  & -1.23    &    7.87             &    5 832    &1.02&   -    \\
Hubble X  & -5.95    &    12.9             &    6 925    &1.02&  -     \\
30Dor     & 265.56*  &    252.79           &    363 059    &0.08&   c    \\
Carina    & -8.83    &    17.89         &   855    &&   d    \\
NGC 346   &          &       31.36           &    112 796   &&       \\
Lagoon    & 3.21 / -6.26 &     8.95 / 7.53    &    566 / 1 176    &&  f / e   \\
Orion     &     -1.25    &     10.43    &    359    &&    g   \\
\end{tabular}\label{tab:Data}
\end{center}
\end{table}

@@

The Carina observations allow us to measure a blue shifted and a red shifted layer \cite{Damiani:2016a}. Also, it is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}; for this sample we show our results. Carina has an index of 1 with a correlation length of 0.55 pc. The structure function shows large-scale oscillatory pattern, with peaks at \(\sim\) 3, 6 and 10 pc. The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.5 pc and a index of 1.15. For this region the structure function reach a constant value of 12 km$^{2}$/s$^{2}$ from 2 to 6 pc. For scales greater than 6 pc large-scale correlation is found up to 15 pc. M42 results shows an index of 0.75 with a correlation length of 0.65.

@@

\cite{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales. High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\). This knots are well fitted with Gaussian profiles thus, defining the kinematic core \cite{munoz1996}. A characteristic radius for them is \(\sim\) 7 pc. \cite{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations. This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\). This scales are related to the presence of strong stellar winds caused by massive stars. For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...

@@

Figure \ref{fig:SF604} shows similarity in our results and previous studies from \cite{tanco1997} and \cite{2019arXiv191203543M} for TAURUS-II data. \citep{2019arXiv191203543M} report $\sigma$ of 7.2 km/s while we have 7.3 km/s. Despite the agreement in observations analysis and interpretations are different. As mentioned by \cite{2019arXiv191203543M} some problems and inconsistencies arise in the results of \cite{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum. None of the previous studies present a power-law index to compare our results, but  Fig. \ref{fig:SF604} shows that the difference lies on the structure function or lag value and no on the form of the plot. With this assumption we can establish the same index of 1.7 for NGC 604 TAURUS-II observations.

@@

The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions. \cite{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc. In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated. There is a good agreement with the results from \cite{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap ours.

%Figure \ref{fig:SFM8} show the structure functions of M8 previously published by \citep{1987ApJ...317..686O} and the structure function computed in this work from observations of \cite{1987A&A...176..338H}.

@@

@@

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/Car}
\caption{Radial velocity map of Carina in H$\alpha$ taken from \cite{Damiani:2016a}.}
\label{fig:MCar}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/M8H.png}
\includegraphics[width=3.5in]{Figures/M8}
\caption{Radial velocity map of M8 in H$\alpha$. Taken from \citep{Damiani:2017b} and \cite{1987A&A...176..338H}.}
\label{fig:MM8}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/OrionL}
\caption{Radial velocity map of Orion in H$\alpha$ taken from \cite{1987A&A...176..347H}.}
\label{fig:MOrion}
\end{figure}

@@

\begin{figure}
\centering 
\includegraphics[width=2in]{Figures/SFplots/M8}
\caption{M8 second-order structure functions for H$\alpha$ emission line \ref{fig:MM8}) from  \cite{Damiani:2017b} and \cite{1987A&A...176..338H}. The figure also shows the structure functions presented in previous works \citep{1987ApJ...317..686O}. Same information as Figure \ref{fig:SF604}.}
\label{fig:SFM8}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2in]{Figures/SFplots/M42}
\caption{M42 second-order structure functions for H$\alpha$ emission line taken from \cite{1987A&A...176..347H} \ref{fig:MOrion}). he figure also shows the structure functions presented in previous works \citep{von1951methode,munch1958internal,arthur2016turbulence}. Same information as Figure \ref{fig:SF604}.}
\label{fig:SFM42}
\end{figure}

>>>>

The procedure using the structure function allow us to determine a distinction between homogeneous turbulence and pure random velocity fluctuations in the photoionized gas, but despite the previous evidence of this fluctuations not been random, little is understood about their nature. Several problems arise in the study of these fluctuation. Intrinsic with observations there is the projection of a three-dimensional function into the plane-of-sky \citep{von1951methode,munch1958internal}. Other statistical techniques like velocity channel analysis (VCA) \citep{2000ApJ...537..720L} have been proved to better recreate the spectrum of the velocity field \citep{medina2014,arthur2016turbulence}. More recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex. \citet{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds. Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \citet{1981MNRAS.194..809L}.

The non-thermal broadening on the spectral emission lines also has been suggested as evidence of disorder motions along the line-of-sight (LOS). \citet{smith1970} discovered that the line width of GEHRs was supersonic in the order of $\sigma \sim$ 17-26 km s\kms. \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$). They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies. The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening. The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}. This features seems to drive visually the regions with filaments, arcs and shells. On their spectra double and multiple emission features are signature of these objects. \citet{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars. \citet{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

Despite different issues that are related with the nature of the problem of turbulence in HII regions, the vast majority of research using the second-order structure function consider individual regions and hence different methodology. \citet{1987ApJ...317..686O} has determined the structure functions for a sample of galactic HII regions but isn't conclusive about them. The individuality of previous works and the need to understand the relationship between the measured turbulent properties for different classes of HII regions has lead us to develop this investigation.

@@

We use data from \citet{1987A&A...176..347H} of the Orion Nebula (M42) located at 440 pc \citep{2008AJ....136.1566O}. Its physical and kinematics properties along its stellar population are well documented in the review of \citet{2001ARA&A..39...99O}. The main ionizing star is $\theta^{1}$Ori C (spectral type $\sim$O7) with fast stellar wind, and 3 B-type stars from the Trapezium cluster. The position of Orion near the side of the Orion Molecular Cloud (OMC-1) make it an ongoing star formation region and a example of a blister HII region \citep{arthur2016turbulence}.

Archival data from \citet{Damiani:2016a} and \citet{Damiani:2017b} are use to study the Carina nebula and Lagoon nebula, respectively.

@@

Using observations observations from \citet{Castro:2018a} (private communication) we study the Tarantula Nebula (30~Dor) in the LMC. At a distance of 49.9 kpc \citep{2013Natur.495...76P} is the most luminous star-forming complex in the Local Group \citep{1984ApJ...287..116K}. The star forming region NGC 2070 host the massive star cluster R136.

@@

The archival data used in this work for the extragalactic giant regions was obtained with the Fabry Perot TAURUS-II instrument in the 4.2-m William Herschel Telescope (WHT) of del Roque de los Muchachos Observatory (ORM) in La Palma, Spain and was retrieved from the La Palma archive\footnote{\url{http://casu.ast.cam.ac.uk/casuadc/ingarch}}. \citet{sabalisck1995supersonic} mentioned the main aspects of the observations (1990 July 31). The two-dimensional imaging spectroscopy was captured using an IPCS-II detector and the 125 $\mu$m etalon. The cumulative integration time per frame is 36 s with a seeing value of 1''. The format of the data cube was of 256*256*100 with a spatial scale of 0.26 pixel$^{-1}$. Finally, the reduction and analysis was done with the packages TAUCAL y TAUFITS \citep{1992ASPC...25..445L}.
The NGC 604 TAURUS-II observations were used by \citet{sabalisck1995supersonic}, \citet{tanco1997} and \citet{2019arXiv191203543M}.

NGC 604 is the brightest giant HII region in the M33 galaxy visually dominated by a big loop, many shells and different size filaments. It is located at the distance of 840 kpc (1'' = 4.1 pc) \citep{2015KamKinematics} with a length of 400 pc. It has a luminosity in L$_{H_\alpha}$ = 10$^{39.42}$ erg s$^{-1}$ \citep{2002MNRAS.329..481B} and in L$_{X}$=9.3$\times$ 10$^{35}$ erg s$^{-1}$ \citep{2008ApJ...685..919T}. \citet{2012ApJ...761....3M} derive an average age of 4$\pm$1 Myr and a total stellar mass of 1.6$^{+1.6}_{-1.0} \times$ 10$^{5}$M$_{\odot}$ for the region.

The stellar population has been identified and classified by \citet{1996ApJ...456..174H} (and references therein). Recently, \citet{2011MNRAS.411..235E} focused on studying the Wolf-Rayet (WR) and red super giants (RSGs) stars population. \citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).  The average ages for the stars, was determined to be from 3 to 5 Myr \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4 $\pm$ 2.1 Myr \citep{2011MNRAS.411..235E}. This suggest that two episodes of star formation, at least, have taken place in the GEHR. \citep{1984A&A...141...49H} identified a gradient from the west to the SE of the nebula of 30 km s$^{-1}$.

NGC 595 is the second brightest giant HII region in the M33 galaxy with a length of 300 pc. The electronic temperature is 7,670 $\pm$116 K \citep{2010MNRAS.402.1635R}. \citet{1983A&A...119..185V} made an estimate of the total masses of HI and HII in the nebula to obtain values of M$_{HI}=$ 1.2 $\times$ 10 $^{6}$ M$_{\odot}$ and M$_{HII} =$ 4.6 $\times$ 10 $^{5}$ M$_{\odot}$, and a ionizing luminosity of the star cluster is estimated at 5 $\times$ 10$^{50}$ erg s $^{1}$. \citet{1996AJ....111.1128M} estimate an age of 4.5 Myrs consistent with \citet{1993AJ....105.1400D}.

It has approximately 250 stars of the OB type, 13 Supergiants and 9 WR \citep{1996AJ....111.1128M}, ten WRs confirmed with spectroscopy \citet{1993AJ....105.1400D}, nine of the WN type and a WC, located near the bright core of the region.

@@

%\citet{2002MNRAS.329..481B} 39.42 38.95 38.21 38.30  39.46 37.36  37.08

@@

\begin{table}
  \begin{center}
    \caption{General statistical properties of the centroid velocities.
      a) \citet{tanco1997}
      b) \citet{2019arXiv191203543M}
      c) \citet{Castro:2018a}
      d) \citet{Damiani:2016a}
      e) \citet{Damiani:2017b}
      f) \citet{1987A&A...176..338H}
      g) \citet{1987A&A...176..347H}.
    } 
\begin{tabular}{cccccc}\hline
HII    &  $\mu$   & $\sigma^{2}$        &  No. of  &\(s_0\)& Previously  \\
   Region       &  [km/s]  &  [km$^{2}$/s$^{2}$] &  points   &[pc]& used in:\\\hline
NGC 604   &  3.56    &    54.63            &    9 510    &1.73&  a,b     \\
NGC 595   &  2.82    &    44.13            &    8 765    &1.73&  -     \\
Hubble V  & -1.23    &    7.87             &    5 832    &1.02&   -    \\
Hubble X  & -5.95    &    12.9             &    6 925    &1.02&  -     \\
30Dor     & 265.56*  &    252.79           &    363 059    &0.08&   c    \\
Carina    & -8.83    &    17.89         &   855    &&   d    \\
NGC 346   &          &       31.36           &    112 796   &&       \\
Lagoon    & 3.21 / -6.26 &     8.95 / 7.53    &    566 / 1 176    &&  f / e   \\
Orion     &     -1.25    &     10.43    &    359    &&    g   \\
\end{tabular}\label{tab:Data}
\end{center}
\end{table}

@@

The Carina observations allow us to measure a blue shifted and a red shifted layer \citet{Damiani:2016a}. Also, it is possible to combine the moments from the sum of two components \citep{2008RMxAA..44..181G}; for this sample we show our results. Carina has an index of 1 with a correlation length of 0.55 pc. The structure function shows large-scale oscillatory pattern, with peaks at \(\sim\) 3, 6 and 10 pc. The galactic region Lagoon nebula \citep{Damiani:2017b} presents a correlation length of 1.5 pc and a index of 1.15. For this region the structure function reach a constant value of 12 km$^{2}$/s$^{2}$ from 2 to 6 pc. For scales greater than 6 pc large-scale correlation is found up to 15 pc. M42 results shows an index of 0.75 with a correlation length of 0.65.

@@

\citet{sabalisck1995supersonic} studied NGC 604 revealing that the kinematics of the region behave different considering different scales. High emission knots on the region encompasses supersonic global velocity dispersion values of 14 $<$ \(\sigma_{LOS}\) $<$ 20 km s\(^{-1}\). This knots are well fitted with Gaussian profiles thus, defining the kinematic core \citet{munoz1996}. A characteristic radius for them is \(\sim\) 7 pc. \citet{yang1996} identified 5 expanding shells within NGC 604, and one of them (Shell 3 on their paper) fall into our observations. This shells is 40 pc in diameter with an expansion velocity above 50 km s\(^{-1}\). This scales are related to the presence of strong stellar winds caused by massive stars. For the NGC 604 case, there is no clear relation between the \(r_0\) and some particular energy injection mechanism...

@@

Figure \ref{fig:SF604} shows similarity in our results and previous studies from \citet{tanco1997} and \citet{2019arXiv191203543M} for TAURUS-II data. \citep{2019arXiv191203543M} report $\sigma$ of 7.2 km/s while we have 7.3 km/s. Despite the agreement in observations analysis and interpretations are different. As mentioned by \citet{2019arXiv191203543M} some problems and inconsistencies arise in the results of \citet{tanco1997}; they don't consider a lower limit based on the observational seeing and that lead them to conclude about a double regime acting on the velocity spectrum. None of the previous studies present a power-law index to compare our results, but  Fig. \ref{fig:SF604} shows that the difference lies on the structure function or lag value and no on the form of the plot. With this assumption we can establish the same index of 1.7 for NGC 604 TAURUS-II observations.

@@

The first attempt at characterizing turbulence in a giant extragalactic HII region, GEHR, was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions. \citet{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc. In the context of the high-resolution observations it is possible to see why their results do not reflect the turbulent structure of the nebula; their observations cover a region where the large-scale velocity fluctuations are uncorrelated. There is a good agreement with the results from \citet{2019arXiv191203543M} (Figure 15 Top on their work), while \citet{1961MNRAS.122....1F} results does not overlap ours.

%Figure \ref{fig:SFM8} show the structure functions of M8 previously published by \citep{1987ApJ...317..686O} and the structure function computed in this work from observations of \citet{1987A&A...176..338H}.

@@

Relationship between plane-of-sky and line-of-sight velocity dispersion.  Comparison with \citet{Rozas:2006b}.

@@

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/Car}
\caption{Radial velocity map of Carina in H$\alpha$ taken from \citet{Damiani:2016a}.}
\label{fig:MCar}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/M8H.png}
\includegraphics[width=3.5in]{Figures/M8}
\caption{Radial velocity map of M8 in H$\alpha$. Taken from \citep{Damiani:2017b} and \citet{1987A&A...176..338H}.}
\label{fig:MM8}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/OrionL}
\caption{Radial velocity map of Orion in H$\alpha$ taken from \citet{1987A&A...176..347H}.}
\label{fig:MOrion}
\end{figure}

@@

\begin{figure}
\centering 
\includegraphics[width=2in]{Figures/SFplots/M8}
\caption{M8 second-order structure functions for H$\alpha$ emission line \ref{fig:MM8}) from  \citet{Damiani:2017b} and \citet{1987A&A...176..338H}. The figure also shows the structure functions presented in previous works \citep{1987ApJ...317..686O}. Same information as Figure \ref{fig:SF604}.}
\label{fig:SFM8}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2in]{Figures/SFplots/M42}
\caption{M42 second-order structure functions for H$\alpha$ emission line taken from \citet{1987A&A...176..347H} \ref{fig:MOrion}). he figure also shows the structure functions presented in previous works \citep{von1951methode,munch1958internal,arthur2016turbulence}. Same information as Figure \ref{fig:SF604}.}
\label{fig:SFM42}
\end{figure}
